A Note on GMM Estimation of Theories of Expectation Formation

### 2019-11-11 notes/GMMResults.tex
Rewrote the draft of the GMMEst note to include results for SV as well as the theoretical derivations of the SV model.

\section{A Generic Framework}

\section{Estimation}
\subsection{Real-time Data}

\subsection{Results}

	\begin{sidewaystable}[t]
		\centering
	\caption{GMM Estimates of Parameters of SE and Inflation Process}
	\label{GMM_Est_SE_Table}
\begin{tabular}{llllllllllll}
	\hline 
	0        & 1  & 2    & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\rho$ & SE: $\sigma$ \\
	\hline 
	Forecast &    &      &     & 0.21                       & 0.01                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
	\hline 
	FE       &    &      &     & 0.18                       & 0.01                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
	\hline 
	Forecast & FE &      &     & 0.2                        & 0.01                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
	\hline 
	Forecast & FE & Disg &     & 0.23                       & 0.05                       & 1          & 0.1          & 0.02                       & 0.03                       & 0.98       & 0.1          \\
	\hline 
	Forecast & FE & Disg & Var & 0.26                       & 0.05                       & 1          & 0.07         & 0.01                       & 0.03                       & 0.98       & 1.11        \\
	\hline 
\end{tabular}
\end{sidewaystable}

\begin{sidewaystable}[t]
	\centering
	\caption{GMM Estimates of Parameters of NI and Inflation Process}
	\label{GMM_Est_NI_Table}
\begin{tabular}{llllllllllllllll}
	\hline 
	0        & 1  & 2    & 3   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\rho$ & NI: $\sigma$ \\
	\hline 
	Forecast &    &      &     & 376.66                    & 1.26                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 0                         & 1.13                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
	\hline 
	FE       &    &      &     & 1.04                      & 159.74                & 0.5                       & 0.5                   & 0.8        & 0.1          & 0                         & 1.26                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
	\hline 
	Forecast & FE &      &     & 1.14                      & 6.74                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 0.59                      & 0.36                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
	\hline 
	Forecast & FE & Disg &     & 1.39                      & 1.46                  & 0.5                       & 0.5                   & 0.8        & 0.1          & 2354.37                   & 10.93                 & 0.5                       & 0.5                   & 0.8        & 0.1          \\
	\hline 
	Forecast & FE & Disg & Var & 1.37                      & 1.1                   & 0.5                       & 0.5                   & 0.8        & 0.1          & 35263.31                  & 332.04                & 0.5                       & 0.5                   & 0.8        & 0.1         \\
	\hline 
\end{tabular}
\end{sidewaystable}

@@

>>>>

@@

\section{Estimation: a Generic Framework}

\subsection{Real-time Data}

\subsection{Results for AR1}

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Parameter Learning for Professionals}
		\label{PL_diag_SPF}
		\includegraphics[width=0.19\textwidth]{figures/spf_pl_est_diag.png}
	\end{subfigure} \\
	\begin{flushleft}
		{\footnotesize Note: the figure plots the predicted moments for a prameter learning (PL) model with AR(1) process of inflation.}
	\end{flushleft}
	\caption{PL of Professionals: Esimated Model Moments and Data Moments}
\end{figure}

	\begin{sidewaystable}[t]
		\centering
	\caption{GMM Estimates of Parameters of SE and Inflation Process}
	\label{GMM_Est_SE_Table}
\begin{tabular}{llllllllllll}
	\hline 
	& 1  & 2    & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(M) & SE: $\rho$ & SE: $\sigma$ \\
	\hline 
	Forecast &    &      &     & 0.05                       & 0.03                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
	FE       &    &      &     & 0.05                       & 0.03                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
	Forecast & FE &      &     & 0.05                       & 0.03                       & 1          & 0.1          & 1                          & 1                          & 1          & 0.1          \\
	Forecast & FE & Disg &     & 0.7                        & 0.38                       & 0.88       & 0.1          & 0.02                       & 0.03                       & 0.98       & 0.1          \\
	Forecast & FE & Disg & Var & 0.7                        & 0.38                       & 0.88       & 0.2          & 0.01                       & 0.03                       & 0.98       & 1.11     \\
	\hline    
\end{tabular}
\end{sidewaystable}

\begin{sidewaystable}[t]
	\centering
	\caption{GMM Estimates of Parameters of NI and Inflation Process}
	\label{GMM_Est_NI_Table}
\begin{tabular}{llllllllllllllll}
	\hline 
	0        & 1   & 2    & 3   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & NI: $\rho$ & NI: $\sigma$ \\
	\hline 
	Forecast &     &      &     & 5.64                      & 804.51                & 0.5                       & 0.5                   & 1          & 0.1          & 93.17                     & 0.64                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
	FE       &     &      &     & 2197.33                   & 60.45                 & 0.5                       & 0.5                   & 1          & 0.1          & 0.62                      & 0.34                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
	Forecast & FE  &      &     & 8565.83                   & 176.23                & 0.5                       & 0.5                   & 1          & 0.1          & 0.62                      & 0.44                  & 0.5                       & 0.5                   & 0.8        & 0.1          \\
	Forecast & FE  & Disg &     & 30.39                     & 353.42                & 0.5                       & 0.5                   & 1          & 0.1          & 3154.03                   & 10.93                 & 0.5                       & 0.5                   & 0.8        & 0.1          \\
	Forecast & FE  & Disg & Var & 2.43                      & 63.03                 & 0.5                       & 0.5                   & 1          & 0.1          & 22970.9                   & 332.03                & 0.5                       & 0.5                   & 0.8        & 0.1          \\
	Disg     & Var &      &     & 90.12                     & 0.56                  & 0.5                       & 0.5                   & 1          & 0.1          & 3297.11                   & 333.49                & 0.5                       & 0.5                   & 0.8        & 0.1       \\
	\hline   
\end{tabular}
\end{sidewaystable}

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Parameter Learning for Households}
		\label{PL_diag_SCE}
		\includegraphics[width=0.19\textwidth]{figures/sce_pl_est_diag.png}
	\end{subfigure} \\
	\begin{flushleft}
		{\footnotesize Note: the figure plots the predicted moments for a prameter learning (PL) model with AR(1) process of inflation.}
	\end{flushleft}
	\caption{PL of Households: Esimated Model Moments and Data Moments}
\end{figure}

\subsection{Results for Stochastic Volatility}

\subsubsection{Professionals Forecasters}

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Estimation of SESV for Professionals}
		\label{SESV_diag_SPF}
		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_sv_diag0.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_sv_diag1.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_sv_diag2.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_sv_diag3.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_sv_diag4.png}
	\end{subfigure}
	\begin{flushleft}
		{\footnotesize Note: this figures plot the data and estimated moments for a  sticky expectation (SE) model with stochastical volatility to inflation. From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively. }
	\end{flushleft}
	\caption{SESV of Professionals: Esimated Model Moments and Data Moments}
\end{figure}

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Estimation of NISV for Professionals}
		\label{NISV_diag_SPF}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_sv_diag0.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_sv_diag1.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_sv_diag2.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_sv_diag3.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_sv_diag4.png}
	\end{subfigure}
	\begin{flushleft}
		{\footnotesize Note: this figures plot the data and estimated moments for a noisy information (NI) model  with stochastical volatility to inflation. From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively. }
	\end{flushleft}
	\caption{NISV of Professionals: Esimated Model Moments and Data Moments}
\end{figure}

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Estimation of SESV for Households}
		\label{SESV_diag_SCE}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_sv_diag0.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_sv_diag1.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_sv_diag2.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_sv_diag3.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_sv_diag4.png}
	\end{subfigure}
	\begin{flushleft}
		{\footnotesize Note: this figures plot the data and estimated moments for a  sticky expectation (SE) model with stochastical volatility to inflation. From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively. }
	\end{flushleft}
	\caption{SESV of Households: Esimated Model Moments and Data Moments}
\end{figure}

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Estimation of NISV for Households}
		\label{NISV_diag_SCE}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_sv_diag0.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_sv_diag1.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_sv_diag2.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_sv_diag3.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_sv_diag4.png}
	\end{subfigure}
	\begin{flushleft}
		{\footnotesize Note: this figure plots the data and estimated moments for a noisy information (NI) model  with stochastical volatility to inflation. From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively. }
	\end{flushleft}
	\caption{NISV of Households: Esimated Model Moments and Data Moments}
\end{figure}

\begin{sidewaystable}[t]
	\centering
	\caption{GMM Estimates of Parameters of SESV}
	\label{GMM_Est_SE_SV_Table}
	\begin{tabular}{llllll}
		\hline 
		0        & 1  & 2    & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SCE}$(M) \\
		\hline 
		Forecast &    &      &     & 0.23                       & 0.01                       \\
		FE       &    &      &     & 0.12                       & 1                          \\
		Forecast & FE &      &     & 0.12                       & 1                          \\
		Forecast & FE & Disg &     & 0.12                       & 1                          \\
		Forecast & FE & Disg & Var & 0.12                       & 1           \\
		\hline               
	\end{tabular}
\end{sidewaystable}

\begin{sidewaystable}[t]
	\centering
	\caption{GMM Estimates of Parameters of NISV}
	\label{GMM_Est_NI_SV_Table}
\begin{tabular}{llllllllllllll}
		\hline 
	0        & 1  & 2    & 3   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & $Var$ & $y$ & Disg & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & $Var$ & $y$ & Disg \\
	\hline 
	Forecast &    &      &     & 0.05                      & 0.02                  & 0.54  & 1   & 5    & 12.09                     & 12.16                 & 0     & 1   & 2    \\
	FE       &    &      &     & 0                         & 0.27                  & 1.06  & 1   & 5    & 130.13                    & 764.51                & 30.99 & 1   & 2    \\
	Forecast & FE &      &     & 0.16                      & 0                     & 1.06  & 1   & 5    & 168.48                    & 695.91                & 43.31 & 1   & 2    \\
	Forecast & FE & Disg &     & 0                         & 0.22                  & 1.06  & 1   & 5    & 166.89                    & 6.1                   & 0.03  & 1   & 2    \\
	Forecast & FE & Disg & Var & 0                         & 0.24                  & 1.07  & 1   & 5    & 362.11                    & 6.26                  & 0.04  & 1   & 2   \\
	\hline 
\end{tabular}
\end{sidewaystable}
